---
title: "Peer Assessment for Regressio Models Coursera.org Course"
author: "Aleksandr Salynskii"
date: "23 Aug 2015"
output: pdf_document
---

##Introduction
Here we'll analyse the relationship between the type of the transmission and MPG(miles per galon) characteristics of the different cars.   
First of all we would use the `mtcars` dataset. 
```{r}
data(mtcars)
```
The `mtcars` dataset contains from 32 automobiles (1973-74 models) on 11 variables.   
`mpg`   -	Miles/(US) gallon   
`cyl`   -  Number of cylinders   
`disp`  -	 Displacement (cu.in.)   
`hp`    -	 Gross horsepower   
`drat`  -	 Rear axle ratio   
`wt`    -	 Weight (lb/1000)   
`qsec`  -	 1/4 mile time   
`vs`    -	 V/S   
`am`    -	 Transmission (0 = automatic, 1 = manual)   
`gear`  -	 Number of forward gears   
`carb`  -	 Number of carburetors   

   
##Analysis
Here we can see the simple distribution of the MPG with type of transmission as the factor.   
```{r}
library(ggplot2)
library(dplyr)
mtcarsMod <- mutate(mtcars, tramsmission = ifelse(am == 0, "Automatic", "Manual"))
mtcarsMod$tramsmission <- as.factor(mtcarsMod$tramsmission)
ggplot(data = mtcarsMod, aes(x = tramsmission, y = mpg, fill = tramsmission)) + 
   geom_boxplot()
```   
   
Here we can see, that the mean of the MPG value is higher in cars with manual transmission instead of automatic.   
Lets fit the linear model to prove it.
```{r}
fit <- lm(mpg ~ am, data = mtcarsMod)
summary(fit)
```
Here we can see, that the cars with manual transmission has additional **7.245** mpg(the value of the Estimate is adding to the mpg result if the transmission type is manual), also we can see, that P value is less than **0.05** so the type of the transmission is significant predictor in this model.   
Now we'll fit some additional models to prove it.
```{r}
round(cor(mtcars), 3)
```
As we know the corr value means the relationship between two values, so for good model we need to use the variables with **minimum** absolute value of the corr index. So as we see in the upper table, the **am** variable has the smallest corr indexes with **vs, qsec, hp, carb** values, so lest try to fit the model with this predictors and compare the result with previous fit.   
```{r}
fit2 <- lm(mpg ~ hp + qsec + vs + am + carb, mtcarsMod)
summary(fit2)
```
Here we can see, that in this model the most significant predictor is **am**, the value of the transmission in this model has the P value smallest P value of **0.00056**, also the **hp** variable seems to be significant because of it's **0.0424** P value. But the R-squared value is much higher than in the model with only transmission type as the predictor.   
Also for the complete analysis we need to fit the full model, with all variables from number of cylinders(`cyl`) to the number of carburetors(`carb`) as the predictors of the outcome value of `mpg`.
```{r}
fitFull <- lm(mpg ~ ., mtcars)
summary(fitFull)
```
The summary of the full model tells us, that there is only one variable hos nearly significant value of the P value, but the R-squared value is much greater than the one we see in the model with only `am` as predictor. 
```{r}
summary(lm(mpg ~ cyl, mtcars))
summary(lm(mpg ~ wt, mtcars))
summary(lm(mpg ~ hp, mtcars))
summary(lm(mpg ~ qsec, mtcars))
summary(lm(mpg ~ carb, mtcars))
```
##Conclusion
As we can see from the analysis part of this work, the transmission factor is significant factor for prediction of the `mpg` value of the car.(Very small P value of the coefficient in the model and the model P value at all.) Also we can say, that the manual transmission add about **7.245** to the `mpg` of the car. But out boxplot tell's us, that only the prediction of the cars with automatic transmission'll be effective instead of manual.